PANCHANGE_analysis

### 2020-09-18 PANCHANGE_analysis.Rmd
deleted the pcl retro regression because it does not exist

PCL:  
Calculate the total GLAD, COPING, RAMP baseline 
## pcl

@@

pcl.percentages.summary
```

@@

Retro-baseline analyses
++CH: need to discuss exclusion criteria
Exclude individuals with NA for MHD, age, gender

```{r Exclusion criteria}

```

```{r exclusion criteria for retro-baseline analysis}
dat.retro <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data"))
  )

@@

++CH: exclusion criteria need double checking
```{r exclusion criteria for prepan-baseline analysis}
dat.prepan <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_march_1_numeric == 1
  )

@@

>>>>

PCL:  
Calculate the total GLAD, COPING, RAMP baseline 
## PCL

@@

kable(pcl.percentages.summary)
pcl.percentages.summary
```

@@

Retro-baseline analyses

```{r subsample for retro-baseline analysis}
dat.retro <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data"))
  )

@@

```{r subsample for prepan-baseline analysis}
dat.prepan <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_march_1_numeric == 1
  )

@@

# PHQ prepan
## Regression: Change scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r phq model0a diff_score prepan}
# Regression coefficients
phq_prepan_model0a_estimates <- model0a.estimates(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model0a_estimates)
phq_prepan_model0a_estimates

# Regression diagnostic statistics
phq_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model0a_reg_stats)
phq_prepan_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r phq model0b diff_score prepan}
# Regression coefficients
phq_prepan_model0b_estimates <- model0b.estimates(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model0b_estimates)
phq_prepan_model0b_estimates

# Regression diagnostic statistics
phq_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model0b_reg_stats)
phq_prepan_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a diff_score prepan}
# Regression coefficients
phq_prepan_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model1a_estimates)
phq_prepan_model1a_estimates

# Regression diagnostic statistics
phq_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model1a_reg_stats)
phq_prepan_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b diff_score prepan}
# Regression coefficients
phq_prepan_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model1b_estimates)
phq_prepan_model1b_estimates

# Regression diagnostic statistics
phq_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(phq_prepan_model1b_reg_stats)
phq_prepan_model1b_reg_stats
```

## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r phq model0a sum_score prepan}
# Regression coefficients
phq_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model0a_explan_estimates)
phq_prepan_model0a_explan_estimates

# Regression diagnostic statistics
phq_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model0a_explan_reg_stats)
phq_prepan_model0a_explan_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r phq model0b sum_score prepan}
# Regression coefficients
phq_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model0b_explan_estimates)
phq_prepan_model0b_explan_estimates

# Regression diagnostic statistics
phq_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model0b_explan_reg_stats)
phq_prepan_model0b_explan_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a sum_score prepan}
# Regression coefficients
phq_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1a_explan_estimates)
phq_prepan_model1a_explan_estimates

# Regression diagnostic statistics
phq_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1a_explan_reg_stats)
phq_prepan_model1a_explan_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_explan_estimates)
phq_prepan_model1b_explan_estimates

# Regression diagnostic statistics
phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_explan_reg_stats)
phq_prepan_model1b_explan_reg_stats
```

# PHQ retro
## Regression: Change scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r phq model0a diff_score retro}
# Regression coefficients
phq_retro_model0a_estimates <- model0a.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model0a_estimates)
phq_retro_model0a_estimates

# Regression diagnostic statistics
phq_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model0a_reg_stats)
phq_retro_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r phq model0b diff_score retro}
# Regression coefficients
phq_retro_model0b_estimates <- model0b.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model0b_estimates)
phq_retro_model0b_estimates

# Regression diagnostic statistics
phq_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model0b_reg_stats)
phq_retro_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a diff_score retro}
# Regression coefficients
phq_retro_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model1a_estimates)
phq_retro_model1a_estimates

# Regression diagnostic statistics
phq_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model1a_reg_stats)
phq_retro_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b diff_score retro}
# Regression coefficients
phq_retro_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model1b_estimates)
phq_retro_model1b_estimates

# Regression diagnostic statistics
phq_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(phq_retro_model1b_reg_stats)
phq_retro_model1b_reg_stats
```

## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r phq model0a sum_score retro}
# Regression coefficients
phq_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model0a_explan_estimates)
phq_retro_model0a_explan_estimates

# Regression diagnostic statistics
phq_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model0a_explan_reg_stats)
phq_retro_model0a_explan_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r phq model0b sum_score retro}
# Regression coefficients
phq_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model0b_explan_estimates)
phq_retro_model0b_explan_estimates

# Regression diagnostic statistics
phq_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model0b_explan_reg_stats)
phq_retro_model0b_explan_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a sum_score retro}
# Regression coefficients
phq_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1a_explan_estimates)
phq_retro_model1a_explan_estimates

# Regression diagnostic statistics
phq_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1a_explan_reg_stats)
phq_retro_model1a_explan_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b sum_score retro}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

# Regression diagnostic statistics
phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1b_explan_reg_stats)
phq_retro_model1b_explan_reg_stats
```

# OCIR prepan
## Regression: Change scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r ocir model0a diff_score prepan}
# Regression coefficients
ocir_prepan_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model0a_estimates)
ocir_prepan_model0a_estimates

# Regression diagnostic statistics
ocir_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model0a_reg_stats)
ocir_prepan_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r ocir model0b diff_score prepan}
# Regression coefficients
ocir_prepan_model0b_estimates <- model0b.estimates(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model0b_estimates)
ocir_prepan_model0b_estimates

# Regression diagnostic statistics
ocir_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model0b_reg_stats)
ocir_prepan_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a diff_score prepan}
# Regression coefficients
ocir_prepan_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model1a_estimates)
ocir_prepan_model1a_estimates

# Regression diagnostic statistics
ocir_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model1a_reg_stats)
ocir_prepan_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b diff_score prepan}
# Regression coefficients
ocir_prepan_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model1b_estimates)
ocir_prepan_model1b_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model1b_reg_stats)
ocir_prepan_model1b_reg_stats
```

## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r ocir model0a sum_score prepan}
# Regression coefficients
ocir_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0a_explan_estimates)
ocir_prepan_model0a_explan_estimates

# Regression diagnostic statistics
ocir_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0a_explan_reg_stats)
ocir_prepan_model0a_explan_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r ocir model0b sum_score prepan}
# Regression coefficients
ocir_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0b_explan_estimates)
ocir_prepan_model0b_explan_estimates

# Regression diagnostic statistics
ocir_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0b_explan_reg_stats)
ocir_prepan_model0b_explan_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a sum_score prepan}
# Regression coefficients
ocir_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1a_explan_estimates)
ocir_prepan_model1a_explan_estimates

# Regression diagnostic statistics
ocir_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1a_explan_reg_stats)
ocir_prepan_model1a_explan_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_explan_estimates)
ocir_prepan_model1b_explan_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_explan_reg_stats)
ocir_prepan_model1b_explan_reg_stats
```

# OCIR retro
## Regression: Change scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r ocir model0a diff_score retro}
# Regression coefficients
ocir_retro_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model0a_estimates)
ocir_retro_model0a_estimates

# Regression diagnostic statistics
ocir_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model0a_reg_stats)
ocir_retro_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r ocir model0b diff_score retro}
# Regression coefficients
ocir_retro_model0b_estimates <- model0b.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model0b_estimates)
ocir_retro_model0b_estimates

# Regression diagnostic statistics
ocir_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model0b_reg_stats)
ocir_retro_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a diff_score retro}
# Regression coefficients
ocir_retro_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model1a_estimates)
ocir_retro_model1a_estimates

# Regression diagnostic statistics
ocir_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model1a_reg_stats)
ocir_retro_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b diff_score retro}
# Regression coefficients
ocir_retro_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model1b_estimates)
ocir_retro_model1b_estimates

# Regression diagnostic statistics
ocir_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model1b_reg_stats)
ocir_retro_model1b_reg_stats
```

## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r ocir model0a sum_score retro}
# Regression coefficients
ocir_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model0a_explan_estimates)
ocir_retro_model0a_explan_estimates

# Regression diagnostic statistics
ocir_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model0a_explan_reg_stats)
ocir_retro_model0a_explan_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r ocir model0b sum_score retro}
# Regression coefficients
ocir_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model0b_explan_estimates)
ocir_retro_model0b_explan_estimates

# Regression diagnostic statistics
ocir_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model0b_explan_reg_stats)
ocir_retro_model0b_explan_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a sum_score retro}
# Regression coefficients
ocir_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1a_explan_estimates)
ocir_retro_model1a_explan_estimates

# Regression diagnostic statistics
ocir_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1a_explan_reg_stats)
ocir_retro_model1a_explan_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b sum_score retro}
# Regression coefficients
ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_estimates)
ocir_retro_model1b_explan_estimates

# Regression diagnostic statistics
ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_reg_stats)
ocir_retro_model1b_explan_reg_stats
```

# PCL prepan
## Regression: Change scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r pcl model0a diff_score prepan}
# Regression coefficients
pcl_prepan_model0a_estimates <- model0a.estimates(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model0a_estimates)
pcl_prepan_model0a_estimates

# Regression diagnostic statistics
pcl_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model0a_reg_stats)
pcl_prepan_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r pcl model0b diff_score prepan}
# Regression coefficients
pcl_prepan_model0b_estimates <- model0b.estimates(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model0b_estimates)
pcl_prepan_model0b_estimates

# Regression diagnostic statistics
pcl_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model0b_reg_stats)
pcl_prepan_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1a diff_score prepan}
# Regression coefficients
pcl_prepan_model1a_estimates <- model1a.estimates(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model1a_estimates)
pcl_prepan_model1a_estimates

# Regression diagnostic statistics
pcl_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model1a_reg_stats)
pcl_prepan_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1b diff_score prepan}
# Regression coefficients
pcl_prepan_model1b_estimates <- model1b.estimates(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model1b_estimates)
pcl_prepan_model1b_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model1b_reg_stats)
pcl_prepan_model1b_reg_stats
```

## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r pcl model0a sum_score prepan}
# Regression coefficients
pcl_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model0a_explan_estimates)
pcl_prepan_model0a_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model0a_explan_reg_stats)
pcl_prepan_model0a_explan_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r pcl model0b sum_score prepan}
# Regression coefficients
pcl_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model0b_explan_estimates)
pcl_prepan_model0b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model0b_explan_reg_stats)
pcl_prepan_model0b_explan_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1a sum_score prepan}
# Regression coefficients
pcl_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1a_explan_estimates)
pcl_prepan_model1a_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1a_explan_reg_stats)
pcl_prepan_model1a_explan_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_explan_reg_stats)
pcl_prepan_model1b_explan_reg_stats
```
